An integrated distance sampling approach for modelling age-structured populations

### 2023-06-02 Manuscript_Nilsen_Nater.qmd
HTML render

---
title: "An open population age structured distance sampling model"
format: docx
author: Erlend B. Nilsen & Chloé Nater
editor: visual
---

@@

### The open population demographic distance sampling model

>>>>

---
title: "An integrated distance sampling approach for modelling age-structured populations"
format: html
author: Erlend B. Nilsen & Chloé R. Nater
editor: visual
bibliography: rypeIDSM_MS1.bib
---

@@

### An integrated age-structured distance sampling model

Distance sampling models have been used for estimating animal abundance in a wide range of contexts and for a variety of taxa (+ref). In recent years, the framework has been extended and also applied for estimating changes in abundance over time in open populations by embedding a hidden state model representing population dynamics [@moore2011; @sollmann2015].
